---
title: "simpleRegress"
author: "Dorothy Decker"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

The bears neck is 20 inches around which helps predict about 57 inches in length. Looking at the accompanying data, it shows that the residual standard error is 5.376, and the R-squared is .7524. 


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 



```{r}
MYCHEST <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(MYCHEST)
summary.lm(MYCHEST)
```

The residual standard error is 4.939 and it is lower than the previous model which was 5.376. In addition, the R-squared is 0.791, which is higher than the previous 0.7524. So by ranking, we can conclude chest is above neck.



```{r}
MYHEADWTH <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(MYHEADWTH)
summary.lm(MYHEADWTH)
```

Now in the third model, the residual standard error is 7.32, which is the highest in comparison to the previous models. In addition, the R-square is now at 0.540, which is smaller than the previous model. Comparing all three models, this ranks the lowest. 




